Dynamics of thin liquid film flows studied with the lattice Boltzmann method

### 2023-07-24 chapters/Paper_five.tex
Chapter two feedback Jens

\section{Theory}\label{sec:theory_five}
The theoretical approach we use to study this system is the lubrication approximation~\cite{Reynolds, oronLongscaleEvolutionThin1997, PhysRevE.63.011208}.
Applying this approximation to the Navier-Stokes equation yields the thin film equation, which for a singular horizontal dimension reads~\cite{RevModPhys.81.739, RevModPhys.81.1131, thielePatternedDepositionMoving2014}
\begin{equation}\label{eq:thin_film_simple}
    \partial_t h = \partial_x \left(\frac{h^3}{3\mu}\partial_x p\right),
\end{equation}
where $\frac{h^3}{3\mu}$ is the mobility $M(h)$\footnote{$m(h) = h^3/3\mu$ is true only for a no-slip velocity boundary condition.}, $h(x,t)$ is the thickness of the film at time $t$ and position $x$, $\mu$ is the liquid's viscosity, and $p$ it's pressure.
The pressure accounts for both the surface tension and the correct fluid substrate behavior (wetting)~\cite{PhysRevE.100.033313}.
We therefore write the pressure as
\begin{equation}\label{eq:pressure_five}
    p = \gamma \partial_x^2 h + \Pi(h),
\end{equation}
where the first term is the (1D) Laplacian of the liquid-vapor interface and $\Pi(h)$ is the disjoining pressure~\cite{oronLongscaleEvolutionThin1997, RevModPhys.81.739, Peschka9275, PhysRevE.63.011208},
\begin{equation}\label{eq:disjoin}
    \Pi(h) = K(\gamma,\theta)\left[\left(\frac{h_{\ast}}{h}\right)^n - \left(\frac{h_{\ast}}{h}\right)^m\right].
\end{equation}
The prefactor $K(\gamma,\theta)\propto \gamma(1-\cos(\theta))$ encodes the wettability and as such the equilibrium contact angle $\theta_{\text{eq.}}$.
This prefactor can be understood as a linking factor to the Hamaker constant ($\mathcal{A}$) with~~\cite{PhysRevE.93.013120, bestehorn20033d, van1988interfacial}
\begin{equation}
    \mathcal{A} = 6\pi h_{\ast}^3 K(\theta).    
\end{equation}
Additionally, $h_{\ast}$ defines the thickness of the precursor layer, therefore the thickness where $\Pi(h_{\ast}) = 0$.
The pair of powers $(n,m)$ need to satisfy $n > m$ and $m > 1$.
For an in deep presentation of the derivation we refer to the work by Schwartz and Eley and Bonn et al.~\cite{SCHWARTZ1998173, RevModPhys.81.739}.

@@

\section{Method}\label{sec:method_five}
\begin{figure}
    \centering
    \includegraphics[width=0.68\textwidth]{graphics/gammas.pdf}
    \caption{Surface tension fields $\gamma(x)$ normalized with $\gamma_0$.
    Different colors and symbols display different surface tensions with $x=0$ is the coordinate of the bridge at $t=0$.
    The surface tension functions are given by Eqs.~(\ref{eq:gamma_const}-\ref{eq:gamma_tanh}).
    }
    \label{fig:gammas}
\end{figure}
We use a computational method, namely the lattice Boltzmann method (LBM), to iteratively solves Eq.~(\ref{eq:thin_with_marangoni}).
The details of the method can be found in the App.~\ref{app:two} and in the references~\cite{PhysRevE.100.033313, PhysRevE.104.034801}.

In addition to the basic lattice Boltzmann algorithm, we require and another force term $F_{\gamma}$ to account for the Marangoni contribution.
Similarly to earlier work on thermal fluctuations~\cite{PhysRevE.104.034801} we construct a force term and match it to the last term in Eq.~\ref{eq:thin_with_marangoni}, 
\begin{equation}\label{eq:force_gamma_grad}
    F_{\gamma} = \frac{3}{2}\partial_x\gamma(x),
\end{equation}
where we have assumed that the surface tension only varies along the horizontal dimension.
With the addition of this force term, our LBM is a numerical algorithm for the system
\begin{equation}\label{eq:lubr2eq1surf}
\begin{cases}
\begin{array}{ll}
\partial_t h + \partial_x (h u)  = 0 & \\ 
\partial_t (h u) = -\frac{1}{\rho_0}h\partial_x p -\nu\alpha_{\delta}(h)u + \frac{3}{2}\partial_x\gamma.
\end{array}
\end{cases}
\end{equation}

Performing the limits discussed in ref.~\cite{PhysRevE.100.033313, PhysRevE.104.034801}, this system becomes an effective solver for Eq~(\ref{eq:thin_with_marangoni}).
Due to the inclusion of $\Pi(h)$, this method allows us to test the non-coalescence criteria for smaller scales, well below $1mm$ droplet diameter~\cite{doi:10.1021/la500459v, karpitschka2014sharp}.

@@

\subsection{Thin film lattice Boltzmann method}\label{app:two}
This approach is based on the evolution of discrete probability density functions ($f_i$) where
\begin{equation}\label{eq:LBE_five}
    \begin{split}
        &f_i(x+c^{(i)}\Delta t,t+\Delta t) = \\
        &\left(1 - \omega\right) f_i(x,t) + \omega f_i^{(eq)}(x,t) + w_i \frac{\Delta t}{c_s^2} c^{(i)} F,
    \end{split}
\end{equation}
where $\omega = \Delta t/\tau_{\ast}$ is a relaxation frequency and $\tau_{\ast}$ is relaxation time. 
The total force acting on the fluid is collected in $F$.
We adopt the standard D1Q3 (one-dimensional) scheme with $3$ lattice velocities~\cite{krueger2017}, given by
\begin{equation}\label{eq:speeds_five}
c^{(i)}  = [0, c, -c], \quad i = 0, 1, 2,
\end{equation}
where the lattice speeds $c=\frac{\Delta x}{\Delta t}$, with weights
\begin{equation}
w_0 = \frac{2}{3},\quad w_{1,2} = \frac{1}{6},
\end{equation}
and the upper bound for information transport, the speed of sound $c_s^2=\frac{c^2}{3}$.
The equilibrium distribution functions $f_i^{(eq)}$ read~\cite{van2010study}:
\begin{gather}
    f_{0}^{eq} = h\left(1-\frac{1}{2c^2}gh - \frac{1}{c^2}u^2\right),\nonumber\\
    f_{1}^{eq} = h\left(\frac{1}{4c^2}gh + \frac{1}{2c}u + \frac{1}{2c^2}u^2\right)\label{eq:equilibria_five},\\
    f_{2}^{eq} = h\left(\frac{1}{4c^2}gh - \frac{1}{2c}u + \frac{1}{2c^2}u^2\right),\nonumber
\end{gather}
where $g$ is the gravitational acceleration that enforces the hydrostatic pressure condition. 
Given the size of the droplet we are interested in, we neglect gravity and set $g=0$ for the remainder of this work.

The film thickness $h$ and the velocity at the free surface $u$ are moments of the distribution functions $f_i$~\cite{Salmon:1999:0022-2402:503, PhysRevE.65.036309, PhysRevE.104.034801}:
\begin{equation}\label{eq:hydrofields_five}
    h= \sum_{i=0}^2 f_i \qquad hu = \sum_{i=0}^2 c^{(i)} f_i.
\end{equation}
The force $F$ in (\ref{eq:LBE_five}) accounts for three terms,
\begin{equation}\label{eq:force_five}
    F = F_{\text{cap}} + F_{\text{fric}} + F_{\gamma}.  
\end{equation}
The first is the effect of the film pressure $p$, Eq.~(\ref{eq:pressure_five}), 
\begin{equation}\label{eq:capillary_force_five}
    F_{\text{cap}} = -\frac{1}{\rho_0} h \frac{\partial p}{\partial x},
\end{equation}
where $\rho_0$ is the fluid density. 
Viscous friction with the substrate is contained in
\begin{equation}\label{eq:fric_force_five}
    F_{\text{fric}} = -\nu \alpha_{\delta}(h) u,
\end{equation}
where $\nu=\mu/\rho_0$ is the fluid kinematic viscosity (related to the relaxation time $\tau$ by $\nu = c_s^2\left(\tau-\frac{\Delta t}{2}\right)$).
The thickness dependent function $\alpha_{\delta}(h)$ is approximately an inverse mobility $M(h)$,
\begin{equation}\label{eq:fric_alpha_five}
     \alpha_{\delta}(h) = \frac{6 h}{2h^2 + 6h\delta + 3\delta^2},
\end{equation}
with a slip length $\delta$.

>>>>

\section{Theory}\label{sec:theory_five}
The theoretical approach we use to study this system is the lubrication approximation~\cite{Reynolds, oronLongscaleEvolutionThin1997, diezGlobalModelsMoving2000}.
Applying this approximation to the Navier-Stokes equation yields the thin film equation, which for a singular horizontal dimension reads~\cite{bonnWettingSpreading2009, crasterDynamicsStabilityThin2009, thielePatternedDepositionMoving2014}
\begin{equation}\label{eq:thin_film_simple}
    \partial_t h = \partial_x \left(\frac{h^3}{3\mu}\partial_x p\right),
\end{equation}
where $\frac{h^3}{3\mu}$ is the mobility $M(h)$\footnote{$m(h) = h^3/3\mu$ is true only for a no-slip velocity boundary condition.}, $h(x,t)$ is the thickness of the film at time $t$ and position $x$, $\mu$ is the liquid's viscosity, and $p$ it's pressure.
The pressure accounts for both the surface tension and the correct fluid substrate behavior (wetting)~\cite{PhysRevE.100.033313}.
We therefore write the pressure as
\begin{equation}\label{eq:pressure_five}
    p = \gamma \partial_x^2 h + \Pi(h),
\end{equation}
where the first term is the (1D) Laplacian of the liquid-vapor interface and $\Pi(h)$ is the disjoining pressure~\cite{oronLongscaleEvolutionThin1997, bonnWettingSpreading2009, peschkaSignaturesSlipDewetting2019, diezGlobalModelsMoving2000},
\begin{equation}\label{eq:disjoin}
    \Pi(h) = K(\gamma,\theta)\left[\left(\frac{h_{\ast}}{h}\right)^n - \left(\frac{h_{\ast}}{h}\right)^m\right].
\end{equation}
The prefactor $K(\gamma,\theta)\propto \gamma(1-\cos(\theta))$ encodes the wettability and as such the equilibrium contact angle $\theta_{\text{eq.}}$.
This prefactor can be understood as a linking factor to the Hamaker constant ($\mathcal{A}$) with~~\cite{diezMetallicthinfilmInstabilitySpatially2016, bestehorn20033d, van1988interfacial}
\begin{equation}
    \mathcal{A} = 6\pi h_{\ast}^3 K(\theta).    
\end{equation}
Additionally, $h_{\ast}$ defines the thickness of the precursor layer, therefore the thickness where $\Pi(h_{\ast}) = 0$.
The pair of powers $(n,m)$ need to satisfy $n > m$ and $m > 1$.
For an in deep presentation of the derivation we refer to the work by Schwartz and Eley and Bonn et al.~\cite{schwartzSimulationDropletMotion1998, bonnWettingSpreading2009}.

@@

\section{Method}\label{sec:method_five}
\begin{figure}
    \centering
    \includegraphics[width=0.68\textwidth]{graphics/gammas.pdf}
    \caption{Surface tension fields $\gamma(x)$ normalized with $\gamma_0$.
    Different colors and symbols display different surface tensions with $x=0$ is the coordinate of the bridge at $t=0$.
    The surface tension functions are given by Eqs.~(\ref{eq:gamma_const}-\ref{eq:gamma_tanh}).
    }
    \label{fig:gammas}
\end{figure}
We use a computational method, namely the lattice Boltzmann method (LBM), to iteratively solves Eq.~(\ref{eq:thin_with_marangoni}).
The details of the method can be found in the App.~\ref{app:two} and in the references~\cite{PhysRevE.100.033313, zitzLatticeBoltzmannSimulations2021}.

In addition to the basic lattice Boltzmann algorithm, we require and another force term $F_{\gamma}$ to account for the Marangoni contribution.
Similarly to earlier work on thermal fluctuations~\cite{zitzLatticeBoltzmannSimulations2021} we construct a force term and match it to the last term in Eq.~\ref{eq:thin_with_marangoni}, 
\begin{equation}\label{eq:force_gamma_grad}
    F_{\gamma} = \frac{3}{2}\partial_x\gamma(x),
\end{equation}
where we have assumed that the surface tension only varies along the horizontal dimension.
With the addition of this force term, our LBM is a numerical algorithm for the system
\begin{equation}\label{eq:lubr2eq1surf}
\begin{cases}
\begin{array}{ll}
\partial_t h + \partial_x (h u)  = 0 & \\ 
\partial_t (h u) = -\frac{1}{\rho_0}h\partial_x p -\nu\alpha_{\delta}(h)u + \frac{3}{2}\partial_x\gamma.
\end{array}
\end{cases}
\end{equation}

Performing the limits discussed in ref.~\cite{PhysRevE.100.033313, zitzLatticeBoltzmannSimulations2021}, this system becomes an effective solver for Eq~(\ref{eq:thin_with_marangoni}).
Due to the inclusion of $\Pi(h)$, this method allows us to test the non-coalescence criteria for smaller scales, well below $1mm$ droplet diameter~\cite{doi:10.1021/la500459v, karpitschka2014sharp}.

@@

\subsection{Thin film lattice Boltzmann method}\label{app:two}
This approach is based on the evolution of discrete probability density functions ($f_i$) where
\begin{equation}\label{eq:LBE_five}
    \begin{split}
        &f_i(x+c^{(i)}\Delta t,t+\Delta t) = \\
        &\left(1 - \omega\right) f_i(x,t) + \omega f_i^{(eq)}(x,t) + w_i \frac{\Delta t}{c_s^2} c^{(i)} F,
    \end{split}
\end{equation}
where $\omega = \Delta t/\tau_{\ast}$ is a relaxation frequency and $\tau_{\ast}$ is relaxation time. 
The total force acting on the fluid is collected in $F$.
We adopt the standard D1Q3 (one-dimensional) scheme with $3$ lattice velocities~\cite{krueger2017}, given by
\begin{equation}\label{eq:speeds_five}
c^{(i)}  = [0, c, -c], \quad i = 0, 1, 2,
\end{equation}
where the lattice speeds $c=\frac{\Delta x}{\Delta t}$, with weights
\begin{equation}
w_0 = \frac{2}{3},\quad w_{1,2} = \frac{1}{6},
\end{equation}
and the upper bound for information transport, the speed of sound $c_s^2=\frac{c^2}{3}$.
The equilibrium distribution functions $f_i^{(eq)}$ read~\cite{vanthangStudy1DLattice2010}:
\begin{gather}
    f_{0}^{eq} = h\left(1-\frac{1}{2c^2}gh - \frac{1}{c^2}u^2\right),\nonumber\\
    f_{1}^{eq} = h\left(\frac{1}{4c^2}gh + \frac{1}{2c}u + \frac{1}{2c^2}u^2\right)\label{eq:equilibria_five},\\
    f_{2}^{eq} = h\left(\frac{1}{4c^2}gh - \frac{1}{2c}u + \frac{1}{2c^2}u^2\right),\nonumber
\end{gather}
where $g$ is the gravitational acceleration that enforces the hydrostatic pressure condition. 
Given the size of the droplet we are interested in, we neglect gravity and set $g=0$ for the remainder of this work.

The film thickness $h$ and the velocity at the free surface $u$ are moments of the distribution functions $f_i$~\cite{salmonLatticeBoltzmannMethod1999, dellarNonhydrodynamicModesPriori2002, zitzLatticeBoltzmannSimulations2021}:
\begin{equation}\label{eq:hydrofields_five}
    h= \sum_{i=0}^2 f_i \qquad hu = \sum_{i=0}^2 c^{(i)} f_i.
\end{equation}
The force $F$ in (\ref{eq:LBE_five}) accounts for three terms,
\begin{equation}\label{eq:force_five}
    F = F_{\text{cap}} + F_{\text{fric}} + F_{\gamma}.  
\end{equation}
The first is the effect of the film pressure $p$, Eq.~(\ref{eq:pressure_five}), 
\begin{equation}\label{eq:capillary_force_five}
    F_{\text{cap}} = -\frac{1}{\rho_0} h \frac{\partial p}{\partial x},
\end{equation}
where $\rho_0$ is the fluid density. 
Viscous friction with the substrate is contained in
\begin{equation}\label{eq:fric_force_five}
    F_{\text{fric}} = -\nu \alpha_{\delta}(h) u,
\end{equation}
where $\nu=\mu/\rho_0$ is the fluid kinematic viscosity (related to the relaxation time $\tau$ by $\nu = c_s^2\left(\tau-\frac{\Delta t}{2}\right)$).
The thickness dependent function $\alpha_{\delta}(h)$ is approximately an inverse mobility $M(h)$,
\begin{equation}\label{eq:fric_alpha_five}
     \alpha_{\delta}(h) = \frac{6 h}{2h^2 + 6h\delta + 3\delta^2},
\end{equation}
with a slip length $\delta$.

### 2023-07-24 chapters/Paper_four.tex
Chapter two feedback Jens

Small amounts of liquid deposited on a substrate are an everyday phenomenon.
From a theoretical point of view this represents a modelling challenge, due to the multiple scales involved: from the molecular interactions among the three phases (solid substrate, liquid film and surrounding gas) to the hydrodynamic flows.
An efficient way to deal with this problem is via the thin-film equation:
\begin{equation}\label{eq:thin_film_Joss}
    \partial_t h = \nabla\cdot(M(h)\nabla p),
\end{equation}
where $h$ is the film thickness, $M(h)$ is a thickness dependent mobility and $p$ is the pressure inside the film.
Solving the thin film equation directly is however a difficult task as it is a fourth order degenerate PDE~\cite{becker2003complex}.
\textit{Swalbe.jl} approaches the problem from a different angle.
Instead of directly solving the thin film equation we use a novel method based on a class lattice Boltzmann models~\cite{krugerLatticeBoltzmannMethod2017}, originally developed to simulate shallow water flows~\cite{Salmon:1999:0022-2402:503}.
This allows us to benefit from the simplicity of the lattice Boltzmann algorithm which makes it straightforward to parallelize the code and run it on accelerator devices.
Choosing appropriate forces it is possible to simulate complex problems.
Among them is the dewetting of a patterned substrates as shown in Fig.~\ref{fig:logo}.
It is as well possible to simulate low contact angle droplets out of equilibrium to probe relaxation experiments, e.g. the Cox-Voinov or Tanner's law~\cite{RevModPhys.81.739}.
Due to a disjoining pressure model for the three phase contact line droplets can not only relax towards their equilibrium they can slide as well~\cite{PhysRevE.100.033313}.
All of this can be coupled with thermal fluctuations to study the stochastic thin film equation~\cite{shah_van_steijn_kleijn_kreutzer_2019}.

@@

An older version of the numerical model (written in C++) has been tested and used for thin film simulations in previous publications~\cite{PhysRevE.100.033313, PhysRevE.104.034801}.
While there is a small performance decrease when moving from C++ with OpenACC to Julia, the benefits of usability, straightforward documentation and automated testing outweighs this issue.
There are many thin film problems the authors will investigate in the future with \textit{Swalbe.jl}.
Among those are switchable substrate and their influence on a dewetting thin film, or the influence of thermal fluctuations on the coalescence of droplets.

@@

That said, the thin film equation is a fourth-order parabolic equation and can of course be solved with appropriate numerical schemes.
Some of these schemes can be found in the refs.~\cite{PhysRevFluids.1.073901, PhysRevE.63.011208, becker2003complex, Peschka9275}.
Upon contacting the authors it should be possible to have access to a working version of the described approach.

@@

Lattice Boltzmann solvers offer another category to approximate the Navier-Stokes equation.
Starting point of this method is not the Navier-Stokes equation but the Boltzmann equation.
Using the Chapman-Enskog expansion~\cite{Chapman, Enskog}, it can be shown that the resulting system of equations recovers to the Navier-Stokes equation.
The method is straightforward to implement and several small to large projects can be found with OSI-approved license. 
To name just a few examples: \href{https://walberla.net/doxygen/index.html}{\textbf{waLBerla}}, \href{https://www.openlb.net/}{\textbf{openLB}} or some smaller project \href{https://gitlab.com/unigehpfs/stlbm}{\textbf{STLBM}}, \href{https://github.com/FrancescaPelusi/TLBfind}{\textbf{TLBfind}} (explicitly written for GPU use).

@@

An interesting problem in the domain of thin liquid films is the coalescence of sessile droplets, see references~\cite{eggers1999coalescence, PhysRevLett.111.144502, PhysRevLett.109.184502, PhysRevLett.95.164503}.
The underlying idea is that two droplets placed on a hydrophilic substrate in close contact to each other will coalesce into a single droplet to minimize their surface area and therefore energy.
The dynamics of this process can be explained using a self-similarity solution of the thin film equation.
In fact, that the bridge height, the point that connects the two droplets, has to grow with a power law.
We now show how to perform that simulation with the help of the \textit{Swalbe.jl} package.
The goal will be to observe a growth of the bridge height as 
\begin{equation}\label{eq:powerlaw}
    h_0(t) = k t^{\alpha},
\end{equation}
where the exponent $\alpha$ should be $2/3$~\cite{doi:10.1063/1.5119014, doi:10.1063/1.4824108}.
This experiment has been performed using the \textit{Pluto notebook} \href{https://jugit.fz-juelich.de/compflu/swalbe.jl/-/blob/JOSS/scripts/Drop_coal.jl}{Drop\_coal.jl}.

>>>>

Small amounts of liquid deposited on a substrate are an everyday phenomenon.
From a theoretical point of view this represents a modelling challenge, due to the multiple scales involved: from the molecular interactions among the three phases (solid substrate, liquid film and surrounding gas) to the hydrodynamic flows.
An efficient way to deal with this problem is via the thin-film equation:
\begin{equation}\label{eq:thin_film_Joss}
    \partial_t h = \nabla\cdot(M(h)\nabla p),
\end{equation}
where $h$ is the film thickness, $M(h)$ is a thickness dependent mobility and $p$ is the pressure inside the film.
Solving the thin film equation directly is however a difficult task as it is a fourth order degenerate PDE~\cite{beckerComplexDewettingScenarios2003}.
\textit{Swalbe.jl} approaches the problem from a different angle.
Instead of directly solving the thin film equation we use a novel method based on a class lattice Boltzmann models~\cite{krugerLatticeBoltzmannMethod2017}, originally developed to simulate shallow water flows~\cite{salmonLatticeBoltzmannMethod1999}.
This allows us to benefit from the simplicity of the lattice Boltzmann algorithm which makes it straightforward to parallelize the code and run it on accelerator devices.
Choosing appropriate forces it is possible to simulate complex problems.
Among them is the dewetting of a patterned substrates as shown in Fig.~\ref{fig:logo}.
It is as well possible to simulate low contact angle droplets out of equilibrium to probe relaxation experiments, e.g. the Cox-Voinov or Tanner's law~\cite{bonnWettingSpreading2009}.
Due to a disjoining pressure model for the three phase contact line droplets can not only relax towards their equilibrium they can slide as well~\cite{PhysRevE.100.033313}.
All of this can be coupled with thermal fluctuations to study the stochastic thin film equation~\cite{shahThermalFluctuationsCapillary2019}.

@@

An older version of the numerical model (written in C++) has been tested and used for thin film simulations in previous publications~\cite{PhysRevE.100.033313, zitzLatticeBoltzmannSimulations2021}.
While there is a small performance decrease when moving from C++ with OpenACC to Julia, the benefits of usability, straightforward documentation and automated testing outweighs this issue.
There are many thin film problems the authors will investigate in the future with \textit{Swalbe.jl}.
Among those are switchable substrate and their influence on a dewetting thin film, or the influence of thermal fluctuations on the coalescence of droplets.

@@

That said, the thin film equation is a fourth-order parabolic equation and can of course be solved with appropriate numerical schemes.
Some of these schemes can be found in the refs.~\cite{PhysRevFluids.1.073901, diezGlobalModelsMoving2000, beckerComplexDewettingScenarios2003, peschkaSignaturesSlipDewetting2019}.
Upon contacting the authors it should be possible to have access to a working version of the described approach.

@@

Lattice Boltzmann solvers offer another category to approximate the Navier-Stokes equation.
Starting point of this method is not the Navier-Stokes equation but the Boltzmann equation.
Using the Chapman-Enskog expansion~\cite{chapmanMathematicalTheoryNonuniform1990, enskogKinetischeTheorieVorgange1917}, it can be shown that the resulting system of equations recovers to the Navier-Stokes equation.
The method is straightforward to implement and several small to large projects can be found with OSI-approved license. 
To name just a few examples: \href{https://walberla.net/doxygen/index.html}{\textbf{waLBerla}}, \href{https://www.openlb.net/}{\textbf{openLB}} or some smaller project \href{https://gitlab.com/unigehpfs/stlbm}{\textbf{STLBM}}, \href{https://github.com/FrancescaPelusi/TLBfind}{\textbf{TLBfind}} (explicitly written for GPU use).

@@

An interesting problem in the domain of thin liquid films is the coalescence of sessile droplets, see references~\cite{eggers1999coalescence, PhysRevLett.111.144502, PhysRevLett.109.184502, PhysRevLett.95.164503}.
The underlying idea is that two droplets placed on a hydrophilic substrate in close contact to each other will coalesce into a single droplet to minimize their surface area and therefore energy.
The dynamics of this process can be explained using a self-similarity solution of the thin film equation.
In fact, that the bridge height, the point that connects the two droplets, has to grow with a power law.
We now show how to perform that simulation with the help of the \textit{Swalbe.jl} package.
The goal will be to observe a growth of the bridge height as 
\begin{equation}\label{eq:powerlaw}
    h_0(t) = k t^{\alpha},
\end{equation}
where the exponent $\alpha$ should be $2/3$~\cite{pawarSymmetricAsymmetricCoalescence2019, doi:10.1063/1.4824108}.
This experiment has been performed using the \textit{Pluto notebook} \href{https://jugit.fz-juelich.de/compflu/swalbe.jl/-/blob/JOSS/scripts/Drop_coal.jl}{Drop\_coal.jl}.
